---
title: "Title"
author: 
- name: "Author"
  affiliations:
    - id: afsc-refm
      name: "Alaska Fisheries Science Center"
      department: "Resource Ecology and Fisheries Management"
      address: 
        - "7600 Sand Point Way N.E."
        - "Seattle, Washington 98115-6349"
date: '`r format(Sys.time(), "%b %e, %Y")`'
fontsize: 11pt 
number-sections: true
number-depth: 3
reference-location: document
reference-section-title: References
bibliography: '`r system.file("files/ExampleBibliog.bib",package="wtsQMD")`'
csl: '`r system.file("files/CJFAS.csl",package="wtsQMD")`'
link-citations: true
crossref:
  chapters: false      # prepend label reference numbers by chater number?
  fig-title: Figure    # for caption: default is "Figure")
  tbl-title: Table     # for caption: default is "Table")
  title-delim: "."     # for caption: default is ":")
  fig-prefix: Figure   # for in-text (use [-@fig-ref] to drop prefix in text)
  tbl-prefix: Table    # for in-text (use [-@tbl-ref] to drop prefix in text)
  fig-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  tbl-labels: arabic    # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  subref-labels: alpha a # options are arabic, roman, roman i, alpha x, alpha X; latter two starting from x/X
  ref-hyperlink: true    # references are hyperlinked if true
format: 
  html: 
    df-print: paged
    toc: true
    toc-location: right
    fig-width: 8
    fig-asp: 1.4
    fig-dpi: 100
    embed-resources: true
    include-in-header: 
      - '`r system.file("files/in-line_math_mode.html",package="wtsQMD")`'
  pdf:
    documentclass: scrartcl
    toc: false
    fig_crop: false
    keep-tex: false
    geometry:
      - left=1.0in
      - right=1.0in
      - top=1.0in
      - bottom=1.0in
      - textwidth=6.5in
      - showframe=false
    include-in-header: 
      - text: |
          \usepackage{placeins}
          \extrafloats{500}
          \maxdeadcycles=10000
          \usepackage{fontspec}
          \usepackage{multicol}
          \usepackage{hhline}
          \newlength\Oldarrayrulewidth
          \newlength\Oldtabcolsep
      - file: '`r system.file("files/ltx_ExtraLatexIncludes.tex",package="wtsQMD")`'
echo: false
warning: false
results: 'hide'
keep-md: true
keep-yaml: false
editor: source
editor_options: 
  chunk_output_type: console
concordance: true
params:
  setup: !expr 'system.file("files/qmd_setup.R",package="wtsQMD")'
  testing: false
  reorderTables: false   #--issue with finding "range" of table values  (don't use)
  reorderFigures: false  #--issue with finding "range" of figure values (don't use)
---
<!-- IMPORTANT: if used as a child doc, all chunk labels must be unique within the overall document -->

<!-- 
  NOTEs: 
     * child_path$peek() gives path to current script.
     * before starting a child document, do 
         "child_path$push(file.path(child_path$peek(),rel_path))" first, 
         where rel_path is the relative path to the child
     * after a child document has finished, do "child_path$pop()" to return to current path value
-->

<!-- if not child doc, set up required objects -->
```{r}
#| label: MAIN_setup
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: "asis"
  testing = params$testing;
  if (testing) cat(params$setup,"\n\n")
  source(params$setup);
  if (testing) cat("root = ",root,"\n\n")
  reorderTables  = params$reorderTables;
  reorderFigures = params$reorderFigures;
```

```{r}
#| label: setup_MAIN
#| results: 'asis'
  require(ggplot2);
  require(kableExtra);
  require(tables);
  Sum = wtsUtilities::Sum;
  old_thm = ggplot2::theme_set(cowplot::theme_cowplot(font_size = 10) +
                               cowplot::background_grid() +
                               cowplot::panel_border());
  thm = wtsPlots::getStdTheme();
  options("readr.show_col_types"=FALSE);
  if (testing) cat("dirThs =",child_path$peek(),"\n\n")

  if (rstudioapi::isAvailable()){
    dirThs = file.path(rstudioapi::getActiveProject(),"Analysis/02_Empirical_Selectivity");
  } else if (child_path$peek()!=""){
    dirThs = child_path$peek();
  } else {
    dirThs = ".";
  }
  ##--NOTE: take out or modify the following as necessary
  if (!exists("s")){
    if (rstudioapi::isAvailable())
      fn = file.path(rstudioapi::getActiveProject(),"rda_ProjectSetup.RData");
    if (child_path$peek()!="")
      fn = file.path(child_path$peek(),"../rda_ProjectSetup.RData");
    #--for debugging: ;
    if (file.exists(fn)) s = wtsUtilities::getObj(fn);
  }
  ##--
```

# Chapter 1 {#sec-Chap1}

Example chapter. The link to the chapter heading is [@sec-Chap1]. 

An example citation is @ref-R, or [@ref-R], depending how entered in qmd file.

An example referrenced equation:

$$ x = y $$ {#eq-XY}

with link [@eq-XY] or Eq. [-@eq-XY].


An example ggplot figure reference is [@fig-Example-ggplot1] (note "fig-" substituted for "fig_" in link name).


```{r fig_Example-ggplot1}
#| results: 'asis'
#| fig-cap: Caption for example ggplot1.
#| fig-width: 6.5
#| fig-asp: 0.5
  dfr = tibble::tibble(x=1:10,y=1:10);
  plt = ggplot(dfr,aes(x=x,y=y)) + geom_point();
  lstFigs = c(lstFigs,wtsQMD::printGGplot(plt,ori="P"));
  
```

Another example ggplot figure reference is Figure [-@fig-Example-ggplot2] (the "Figure" is dropped from the link).

```{r fig_Example-ggplot2}
#| results: 'asis'
#| fig-width: 9
#| fig-asp: 0.6
  dfr = tibble::tibble(x=1:10,y=1:10);
  plt = ggplot(dfr,aes(x=x,y=y)) + geom_point();
  cap = "Caption for example ggplot2.";
  lstFigs = c(lstFigs,wtsQMD::printGGplot(plt,cap=cap,ori="L"));
  
```

An example table is shown in Table [-@tbl-XY].

```{r}
#| results: 'asis'
  kbl = kableExtra::kbl(dfr);
  cap = "Example table."
  lstTbls = c(lstTbls,
              wtsQMD::insertKblIntoQMD(kbl,
                                       lbl="tbl-XY", 
                                       cap=cap,
                                       ori="P"));
```

A base R plot is shown in Figure  [-@fig-Example-baseRplot].

```{r fig_Example-baseRplot}
#| results: 'asis'
#| fig-cap: Caption for example base R plot example.
#| fig-width: 6.5
#| fig-asp: 0.5
  dfr = tibble::tibble(x=1:10,y=1:10);
  lstFigs = c(lstFigs,wtsQMD::printRGraphics(expression(plot(dfr$x,dfr$y)),ori="P"));
  
```

<!-- # Chapter 2 {#sec-Chap2} -->
<!--```{r main_Chap2, child=file.path(child_path$peek(),"q02_Chap2.qmd"),eval=TRUE}-->
<!--````-->

<!-- references -->
```{r,eval=!knitr::opts_knit$get("child")&(!isPDF),results='asis'}
  cat("# References {-}\n");
  cat("::: {#refs}\n");
  cat(":::\n\n");
```

<!-- tables, if not child doc and lstTbls is not empty -->
```{r}
#| label: tables_MAIN
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printTablesSectionFromList.R",package="wtsQMD"));
```

<!-- figures, if not child doc and lstFigs is not empty -->
```{r}
#| label: figures_MAIN
#| eval: !expr '!knitr::opts_knit$get("child")'
#| results: asis
  source(system.file("files/printFiguresSectionFromList.R",package="wtsQMD"));
```

